 extracting environmenal and oceanographic variables

### 2023-05-12 03_environ_var.Rmd
saves fulltracks to hard drive and data folder

Save final buoy df for analysis use next.
```{r}
saveRDS(tracks_SS_10, 'data/fulltrack10.rda')
saveRDS(tracks_SS_12, 'data/fulltrack12.rda')
saveRDS(tracks_SS_13, 'data/fulltrack13.rda')
saveRDS(tracks_SS_14, 'data/fulltrack14.rda')
saveRDS(tracks_SS_16, 'data/fulltrack16.rda')
saveRDS(tracks_SS_18, 'data/fulltrack18.rda')
saveRDS(tracks_SS_19, 'data/fulltrack19.rda')
saveRDS(tracks_SS_20, 'data/fulltrack20.rda')
saveRDS(tracks_SS_21, 'data/fulltrack21.rda')
saveRDS(tracks_SS_22, 'data/fulltrack22.rda')
saveRDS(tracks_SS_23, 'data/fulltrack23.rda')
saveRDS(tracks_SS_07, 'data/fulltrack07.rda')
saveRDS(tracks_SS_08, 'data/fulltrack08.rda')
```

>>>>

Save final buoy df for analysis use next.
```{r}
saveRDS(tracks_SS_10, 'data/fulltrack10.rda')
saveRDS(tracks_SS_12, 'data/fulltrack12.rda')
saveRDS(tracks_SS_13, 'data/fulltrack13.rda')
saveRDS(tracks_SS_14, 'data/fulltrack14.rda')
saveRDS(tracks_SS_16, 'data/fulltrack16.rda')
saveRDS(tracks_SS_18, 'data/fulltrack18.rda')
saveRDS(tracks_SS_19, 'data/fulltrack19.rda')
saveRDS(tracks_SS_20, 'data/fulltrack20.rda')
saveRDS(tracks_SS_21, 'data/fulltrack21.rda')
saveRDS(tracks_SS_22, 'data/fulltrack22.rda')
saveRDS(tracks_SS_23, 'data/fulltrack23.rda')
saveRDS(tracks_SS_07, 'data/fulltrack07.rda')
saveRDS(tracks_SS_08, 'data/fulltrack08.rda')

# also saves to external hard drive
saveRDS(tracks_SS_10, 'D:/Buoy_dfs/fulltrack10.rda')
saveRDS(tracks_SS_12, 'D:/Buoy_dfs/fulltrack12.rda')
saveRDS(tracks_SS_13, 'D:/Buoy_dfs/fulltrack13.rda')
saveRDS(tracks_SS_14, 'D:/Buoy_dfs/fulltrack14.rda')
saveRDS(tracks_SS_16, 'D:/Buoy_dfs/fulltrack16.rda')
saveRDS(tracks_SS_18, 'D:/Buoy_dfs/fulltrack18.rda')
saveRDS(tracks_SS_19, 'D:/Buoy_dfs/fulltrack19.rda')
saveRDS(tracks_SS_20, 'D:/Buoy_dfs/fulltrack20.rda')
saveRDS(tracks_SS_21, 'D:/Buoy_dfs/fulltrack21.rda')
saveRDS(tracks_SS_22, 'D:/Buoy_dfs/fulltrack22.rda')
saveRDS(tracks_SS_23, 'D:/Buoy_dfs/fulltrack23.rda')
saveRDS(tracks_SS_07, 'D:/Buoy_dfs/fulltrack07.rda')
saveRDS(tracks_SS_08, 'D:/Buoy_dfs/fulltrack08.rda')
```
